01 Calculating Travel Time for TTS16 OD

### 2023-11-24 data-raw/05-TTS16-Calculating-Travel-Time-OD-GGH4.Rmd
Updated with code to write od_ggh4_mode_purpose to arrow parquet

Libraries:
```{r setup, include=FALSE}
library(disk.frame) # not installed on this machine
library(dplyr) # A Grammar of Data Manipulation
library(ggplot2) # Create Elegant Data Visualisations Using the Grammar of Graphics
library(gridExtra) # Miscellaneous Functions for "Grid" Graphics
library(httr) # Tools for Working with URLs and HTTP
library(knitr) # A General-Purpose Package for Dynamic Report Generation in R
#install.packages("kableExtra", dependencies = TRUE) #installing kableExtra and dependencies as I was receiving errors
library(kableExtra) # Construct Complex Table with 'kable' and Pipe Syntax
# install.packages("devtools")
# install.packages("Rtools")
# devtools::install_github("https://github.com/hrbrmstr/lodes.git", dependencies = TRUE) # if you need to download
#library(lodes) # not installed on this machine
library(progress) # Terminal Progress Bars
library(purrr) # Functional Programming Tools
library(sf) # Simple Features for R
library(stplanr) # not installed on this machine
library(tidycensus) # not installed on this machine
library(tidyr) # Tidy Messy Data
library(tmap) # Thematic Maps
library(zoo) # for rollapplyr

# setup options
setup_disk.frame() # setup disk.frame parallel computing
options(future.globals.maxSize = Inf) # allow disk.frame threads to talk to eachother without limits
tmap_mode("plot")
```

@@

##--- Prepare Input Data
loading the destination points and origins points:
```{r}
load(file = "TTS16-data-inputs/Travel-Time-Calculations/inputs/work_origins.Rdata")
load(file = "TTS16-data-inputs/Travel-Time-Calculations/inputs/job_destinations.Rdata")
```

@@

```{r download data, include=FALSE, eval=FALSE}
#downloading ontario osm in the correct format
download.file(url = paste0("https://download.geofabrik.de/north-america/canada/ontario-latest.osm.pbf"),
              destfile = file.path(r5_path, "osm.pbf"),
              mode = "wb")

@@

>>>>

Libraries:
```{r setup, include=FALSE}
library(disk.frame) # not installed on this machine
library(dplyr) # A Grammar of Data Manipulation
library(ggplot2) # Create Elegant Data Visualisations Using the Grammar of Graphics
library(gridExtra) # Miscellaneous Functions for "Grid" Graphics
library(httr) # Tools for Working with URLs and HTTP
library(knitr) # A General-Purpose Package for Dynamic Report Generation in R
library(kableExtra) # Construct Complex Table with 'kable' and Pipe Syntax
library(progress) # Terminal Progress Bars
library(purrr) # Functional Programming Tools
library(sf) # Simple Features for R
library(stplanr) # not installed on this machine
library(tidycensus) # not installed on this machine
library(tidyr) # Tidy Messy Data
library(tmap) # Thematic Maps
library(TTS2016R)
library(zoo) # for rollapplyr

# setup options
setup_disk.frame() # setup disk.frame parallel computing
options(future.globals.maxSize = Inf) # allow disk.frame threads to talk to each other without limits
tmap_mode("plot")
```

@@

##--- Prepare Input Data

Prepare destination points and origins points:
```{r}
data("ggh_taz_v4")

coords <- ggh_taz_v4 |>
  st_transform(crs = 4326) |>
  st_centroid() |>
  st_coordinates()

work_origins <- ggh_taz_v4 |>
  st_drop_geometry() |>
  transmute(id = GGHV4,
            lon = coords[,1],
            lat = coords[,2])

job_destinations <- work_origins
```

@@

Version of data downloaded:

```{r download data, include=FALSE, eval=FALSE}
#downloading ontario osm in the correct format
download.file(url = paste0("https://download.openstreetmap.fr/extracts/north-america/canada/ontario/golden_horseshoe-latest.osm.pbf"),
              destfile = file.path(r5_path, "osm.pbf"),
              mode = "wb")

@@

<!-- QUESTION FOR RAFA ET AL. IS IT POSSIBLE TO HAVE MULTIPLE osm.pbf FILES IN THE SAME DIRECTORY AND CALL THEM BY NAME? -->
